\documentclass[11pt]{article}
\PassOptionsToPackage{hyphens}{url}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{array}
\sloppy
\usepackage{style/meta_report}

\title{Hybrid Latent Grokking:\\Mechanistic Interpretability Across a Model Ladder}
\author{%
  Aditya Kumar Pandey\thanks{Bytesflow AI. \texttt{aditya@bytesflow.ai}. Led research design, training experiments, and mechanistic analysis.} \and
  Anuj Kumar Pandey\thanks{Bytesflow AI. \texttt{anuj@bytesflow.ai}. Helped write the code, create the figures, and write the paper draft.}%
}
\date{}

\IfFileExists{metrics_hybrid.tex}{\input{metrics_hybrid.tex}}{%
  \IfFileExists{metrics.tex}{\input{metrics.tex}}{%
    \newcommand{\HybridNandaAcc}{TBD}
    \newcommand{\HybridMinimalAcc}{TBD}
    \newcommand{\HybridFullAcc}{TBD}
    \newcommand{\HybridNandaFVE}{TBD}
    \newcommand{\HybridMinimalFVE}{TBD}
    \newcommand{\HybridFullFVE}{TBD}
    \newcommand{\HybridNandaFVEAdaptive}{TBD}
    \newcommand{\HybridMinimalFVEAdaptive}{TBD}
    \newcommand{\HybridFullFVEAdaptive}{TBD}
    \newcommand{\HybridNandaSeedsClean}{0}
    \newcommand{\HybridMinimalSeedsClean}{0}
    \newcommand{\NandaAdaptiveKRange}{--}
    \newcommand{\BMIKeyFreqs}{TBD}
    \newcommand{\BMIWLKeyFreqs}{TBD}
    \newcommand{\BMITestAcc}{TBD}
    \newcommand{\BMIFullTestCE}{TBD}
    \newcommand{\BMITrigTestCE}{TBD}
    \newcommand{\BMIExcludedTestCE}{TBD}
    \newcommand{\BMIFVEMean}{TBD}
    \newcommand{\BMIEmGini}{TBD}
    \newcommand{\BMINSeeds}{5}
  }%
}

\begin{document}
\maketitle

\begin{abstract}
We study grokking in a three-model ladder on modular addition ($P{=}113$): a Nanda-style one-layer MLP, a minimal Tiny Recursive Model (TRM), and a full ACT-based TRM (50{,}000 steps, $\BMINSeeds$ seeds).
Before extending TRM training, we run Ren-style mechanistic probes \citep{ren2026reasoning} on 20k checkpoints to separate Nanda cleanup from latent guessing.
The Nanda MLP calibrates our progress-measure stack: under a data-driven key-frequency count (matching \citealp{nanda2023progress}), all $\HybridNandaSeedsClean$/$\BMINSeeds$ seeds reach faithful trig-FVE $\geq 0.95$ (mean $\HybridNandaFVEAdaptive$); a fixed five-frequency reconstruction under-reports this to $\HybridNandaFVE$.
Minimal TRM reaches Nanda-grade sparse Fourier structure on $\HybridMinimalSeedsClean$/$\BMINSeeds$ seeds at the final checkpoint (adaptive FVE $\approx 0.99$); three seeds collapse under post-grokking cleanup (adaptive mean $\HybridMinimalFVEAdaptive$).
Full TRM groks ($\HybridFullAcc$ test accuracy) but does not form the Fourier circuit (adaptive FVE mean $\HybridFullFVEAdaptive$); Ren probes show fixed-point violation and ACT-depth guessing.
We report final, grokking, and best-FVE checkpoints, adaptive FVE calibration, all-frequency ablations, per-neuron tables, and Nanda-style phase plots.
\end{abstract}

\input{sections/introduction}
\input{sections/methods}
\input{sections/calibration_nanda}
\input{sections/trm_minimal_main}
\input{sections/full_trm_extension}
\input{sections/ren_diagnosis}
\input{sections/related_work}
\input{sections/limitations}

\appendix
\input{appendix}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
